Combining formal and distributional models of predicate semantics

### 2016-03-10 papers/acl2016/paper.tex
Minor update to the paper (probably incorrect, though, as I am rerunning some of those experiments...)
Former-commit-id: 52339c6aaf7c567134a64e5e8ae7785ad23326af

Some related work on including structured information in distributional
representations: Manaal's retrofitting semantic lexicons, Sebastian Riedel's
``Injecting Logical Background Knowledge into Embeddings for Relation
Extraction'', work on PRA and KBC more generally\ldots Also, the whole line of
work on knowledge base embeddings (RESCAL, TransE, etc.) is at least slightly
relevant here, as is PRA.  \mattnote{Actually write this section}.

@@

\tabref{dev-results} shows the results of our experiments on the development
set (the same as the test set used by Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}).  As can be
seen, the combined model significantly improves performance, giving a 42\%
relative increase in MAP over the distributional-only baseline.  This table
also shows the benefit of using our modified logical forms (see
\secref{better-lfs}); by being able to better model the relations between
entities, MAP of all of the models is significantly improved.

>>>>

Some related work on including structured information in distributional representations: Manaal's
retrofitting semantic lexicons, Sebastian Riedel's ``Injecting Logical Background Knowledge into
Embeddings for Relation Extraction'', work on PRA and KBC more generally\ldots Also, the whole line
of work on knowledge base embeddings (RESCAL, TransE, etc.) is at least slightly relevant here, as
is PRA.  And all of the semantic parsing approaches that go from text to a pseudo-logical form,
then to an actual Freebase query (Kwiatkowski, Reddy's TACL paper, Liang?) \mattnote{Actually write
this section}.

@@

\tabref{dev-results} shows the results of our experiments on the development
set (the same as the test set used by Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary}).  As can be
seen, the combined model significantly improves performance, giving a 42\%
relative increase in MAP over the distributional-only baseline.  This table
also shows the benefit of using our modified logical forms (see
\secref{better-lfs}); by being able to better model the relations between
entities, MAP of all of the models is significantly improved.\footnote{Because
of the large amount of annotation effort involved, we did not include the
unique results from this run in the evaluation pool.  It is possible that this
had the effect of lowering the MAP score for these methods.  However, the large
majority of the predictions made by these methods were already annotated, and
spot-checking the unannotated ones showed that practically all of the unique
predictions made in this scenario were incorrect, and thus annotating them
would not change the score.}
